Evaluation of Machine Translation Pre-Trained Models for Many-to-English Translation

### 2024-08-22 paper/paper.tex
finalised

Sentences typically consist of everyday phrases such as 'I have to go to sleep', 'That is intriguing', and 'Where do you live?'. They may also include single-word exclamations like 'Speak!', 'So what?', or 'Look!'. Additionally, multiple sentences such as 'You may write in any language you want. On Tatoeba, all languages are considered equal', and 'Guns don't kill people. People kill people' can be found inside the corpus. A few of them also include human names, 'Compare your answer with Tom's', and 'Muiriel is 20 now'. All the sentences seem to be straightforward and literal, without any use of linguistic features such as metaphors or sarcasm. Figure \ref{table:parallel_sentence} shows a couple of examples of parallel sentences in the final dataset, across all 14 languages and the original English sentence.

@@

The METEOR implementation in this study through the NLTK library is based on the original METEOR paper \cite{lavie-2007-meteor}, which is described as "relatively simple and naive." A newer version, METEOR-1.5 \cite{denkowski-lavie-2014-meteor-universal} offers improved features and has been reported to produce significantly different results \cite{tuetschek-2021-meteor-issue-nltk}. Therefore, reevaluating translation models using the updated metric could be beneficial.

>>>>

Sentences typically consist of everyday phrases such as 'I have to go to sleep', 'That is intriguing', and 'Where do you live?'. They may also include single-word exclamations like 'Speak!', 'So what?', or 'Look!'. Additionally, multiple sentences such as 'You may write in any language you want. On Tatoeba, all languages are considered equal', and 'Guns don't kill people. People kill people' can be found inside the corpus. A few of them also include human names, 'Compare your answer with Tom's', and 'Muiriel is 20 now'. All the sentences seem to be straightforward and literal, without any use of linguistic features such as metaphors or sarcasm. A word cloud is illustrated in Figure \ref{fig:wordcloud}, while Figure \ref{table:parallel_sentence} shows a couple of examples of parallel sentences in the final dataset, across all 14 languages and the original English sentence.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/wordcloud.png}
    \caption{Dataset word cloud illustrated.}
    \label{fig:wordcloud}
\end{figure}

@@

The METEOR implementation in this study through the NLTK library is based on the original METEOR paper \cite{lavie-2007-meteor}, which is described as "relatively simple and naive." A newer version, METEOR-1.5 \cite{denkowski-lavie-2014-meteor-universal} offers improved features and has been reported to produce significantly different results \cite{tuetschek-2021-meteor-issue-nltk}. Therefore, re-evaluating translation models using the updated metric might be beneficial. Experimenting with other metrics such as chrF \cite{popovic-2015-chrf}, which is widely used by Meta AI \cite{nllb200-2020} could also provide a more comprehensive evaluation.
